\let\cleardoublepage\clearpage
\chapter{Conclusion}
\section{Analysis}
This thesis has demonstrated how to build an intelligent application based on Semantic Web technologies. News were picked as a use case for this project. They posed the challenge to extract their meaning as being free and unstructured text about any kind of subject or area of life, expressing facts, opinions and conclusions from various different topics and categories. The solution that was presented was based partly on text mining partly on semantic technologies. A semantic news pipeline was presented that included processing steps ranging from raw text entity extraction to conversion to RDF data, interlinked with other Linked Open Data data sets, that enabled writing news aggregation SPARQL queries, against a triplestore repository with the data imported, to really get proper insight about trends of popularity of entities, mentioned in the news.

Finally the results of the news aggregation were presented in the form of SVG-based visualisations as word clouds and geographic heat maps with the user's ability to choose a news category of interest, dates for news published in that period and the option to choose between direct popularity or relative popularity normalized within the last year.

\section{Future directions}
Possible improvements to the \textit{Semantic News Map} could be adding a user base which will keep information about news preferences and also could store rendered visualisations as "Favourites" in your account. News details view could be reworked to be more interactive. More experiments could be done with interesting data sets about, e.g. company information (offshore companies, owners, shareholders, etc.). 

The power of semantics is limitless. It has the unique property to put the world's knowledge under your disposal and actually give you real insight about it. In a world where information is the most valued asset, this technology is priceless. I truly hope that its popularity will continue to grow so that every person on this world could benefit from it.